-
# Report of *ncappc* package [*]
-
------------------------------------------------------------------

==============================================================

```{r main, echo=FALSE}
arglist <- fnOut$arglist
txt     <- fnOut$TXT
pddf    <- fnOut$pddf
prnTab  <- fnOut$prnTab
spread  <- fnOut$spread
conc    <- fnOut$conc
histobs <- fnOut$histobs
sprtxt  <- ifelse(spread=="ppi", "95% parametric prediction interval of the NCA metrics obtained from the simulated data", "95% nonparametric prediction interval of the NCA metrics obtained from the simulated data")
```

-

Summary of the data set and the results
-------------------------------


```{r txt, echo=FALSE}
cat(txt)
```

-

```{r table, echo=FALSE, results='asis'}
kable(pddf, align='c')
```

-------------------------------
-
Command-line arguments passed to ncappc function
-------------------------------

```{r cmd, echo=FALSE}
print(arglist)
```


------------------------------
-
Description of the tabular output
------------------------------

**Table 1 (ncaOutput.tsv).** Estimated NCA metrics using the observed and simulated concentration-time profile. Brief description of the column names: **ID** = individual ID, **AUClast** = AUC from the time of dose to the time of the last sampled plasma concentration estimated from the observed data. Similar annotation was used for the other NCA metrics.

# Table 1. ncaOutput.tsv (selected columns of top 100 rows)

```{r Final table, echo=FALSE, results='asis'}
require(xtable)
print(xtable(prnTab, align=rep("c",ncol(prnTab)+1), rotate.colnames = T), include.rownames=FALSE, type = 'html')
```

**Table 2 (Obs_Stat.tsv).** A set of statistical parameters calculated for the population groups for Tmax, Cmax, AUClast, AUClower_upper, AUCINF_obs, AUC_pExtrap_obs, AUCINF_pred, AUC_pExtrap_pred, AUMClast, AUMCINF_obs, AUMC_pExtrap_obs, AUMCINF_pred, AUMC_pExtrap_pred, HL_Lambda_z, Rsq, Rsq_adjusted, No_points_Lambda_z obtained from the observed data. Brief description of the calculated statistical parameters: **Ntot** = Total number of data points, **Nunique** = number of unique data points, **Min** = minimum value, **Max** = maximum value, **Mean** = mean/average value, **SD** = standard deviation, **SE** = standard error, **CVp** = coefficient of variation %, **a95CIu** = upper limit of 95% arithmetic confidence interval, **a95CIl** = lower limit of 95% arithmetic confidence interval, **gMean** = geometric mean, **gCVp** = geometric coefficient of variation %.


-
---------------------------------
Description of the graphical output
------------------------------

```{r plot, echo=FALSE, fig.align='center', dpi=80}
if (length(conc)>0){
  for (i in 1:length(conc)){suppressMessages(suppressWarnings(grid.draw(conc[[i]]))); Sys.sleep(0.5); grid.newpage()}
}else{
  print("No concentration vs time plot is available.")
}
```

**Figure 1.** [Individual level] Concentration vs time profile for each individual stratified by dose or population group, if any, as obtained from the observed data. The left panels represent the raw data, while the right panels represent the semi-logarithmic form of the concentration data. Each of the lines represents individual data.

-

```{r histobsplot, echo=FALSE, fig.align='center',fig.height=8, fig.width=6, dpi=100}
if (length(histobs)>0){
  for (i in 1:length(histobs)){suppressMessages(suppressWarnings(grid.draw(histobs[[i]]))); Sys.sleep(0.5); grid.newpage()}
}else{
  print("No histogram is available as the number of individuals is less than 5 in each population strata!")
}
```

**Figure 2.** [Population level] Histogram of four selected NCA metrics (AUClast, AUCINF_obs, Cmax, Tmax) estimated from the observed data. The solid blue vertical and dotted lines represent the population mean and the "spread" of the data. The "spread" is defined by `r print(sprtxt)` of the NCA metrics obtained from the study population.



-
[*] Created and maintained by:
### Chayan Acharya, Andrew C. Hooker, Siv Jonsson, Mats O. Karlsson
### *Department of Pharmaceutical Biosciences*
### *Uppsala University, Sweden*

